17th International Satisfiability Modulo Theories Competition (SMT-COMP 2022): Rules and Procedures

### 2022-05-16 rules/rules22.tex
pass over proof track section

In the \prooftrack, teams can submit proof-producing solvers together
with a proof checker for their proof format.  We will compile and
present the results, as well as assemble a panel of non-organizer
experts to do a qualitative assessment for each proof-producing
solver, proof format, and proof checker.

@@

\header{Input/Output Solver.}
For the \prooftrack, solver authors should provide two scripts
with their solver.  The first script
\texttt{starexec\_solver\_default} takes the name of the benchmark file as
single argument and should run the solver on the benchmark.
As described in Section~\ref{sec:logistics}, the benchmark
contains the commands \akey{(check-sat)} and \akey{(get-proof)}.
The solver must output the answers to both of these commands to stdout.
Output to stderr is ignored by the toolchain.

Solvers must respond to each command in the benchmark script with the
answers defined in the SMT-LIB format specification.  If the solver
outputs a proof, this proof must be an s-expression according to the
SMT-LIB standard, but the format is not specified further.  Solvers
that respond \texttt{unknown} to the \akey{check-sat} command should
respond with an error to the following \akey{get-proof} command.  Note
that the SMT-LIB conformant error result should be output to stdout.

\header{Input/Output Checker.}
The second script \texttt{starexec\_checker\_default} takes as input
the benchmark file name as first argument and the proof output of the
solver script as second argument.  Note that this proof output will
usually start with the \texttt{unsat} result of the \akey{(check-sat)}
command, which the checker must either parse or skip.

The checker should check the provided proof and provide the result to
stdout.  Result printed to stderr is ignored.  The first line of the
proof checker should be one of \texttt{valid}, \texttt{invalid},
\texttt{holey}, \texttt{sat}, \texttt{unknown}.  The answer \texttt{valid}
must only be given, if the checker made sure using the proof that the
benchmark is unsat.  A checker that returns \texttt{valid} to a
satisfiable benchmark is deemed to be unsound.  The answer
\texttt{invalid} should be returned if the proof is errorneous or
otherwise malformed.  If the proof is correct but skips some proof
steps or if side-conditions for a rule are not checked by the proof
checker, the answer should be \texttt{holey}.  The answer \texttt{sat}
should be given if the solver claimed that the benchmark is
satisfiable and \texttt{unknown} should be given, if the solver answered
\texttt{unknown} or if it did not give a proof or gave an error result.

After this firsts line, the proof checker can give arbitrary
\texttt{key=value} pairs after the results.  These will
be collected in the final result table and can include information
about the number of proof steps, the number of nodes in the proof, the
number of holes, the number of different proof rules, etc.

\header{Result.}
The result of a solver is considered \emph{erroneous} if (i) the
response to the \akey{check-sat} command is \texttt{sat} and the
benchmark is unsat, (ii) the proof checker returns \texttt{invalid} to
the given proof.  Because the \prooftrack is non-competitive and
because there is no common definition of a valid proof, there will be
no score computed for this track.

>>>>

In the \prooftrack, teams can submit a proof-producing solver together with a
proof checker for its proof format.  We will compile and present the results, as
well as assemble a panel of experts (not necessarily organizers) to do a
qualitative assessment for each proof-producing solver, proof format, and proof
checker.

@@

\header{Input/Output Solver.}
For the \prooftrack, solver authors should provide two scripts
with their solver.  The first script,
\texttt{starexec\_solver\_default}, should take the name of the benchmark file as
a single argument and run the solver on the benchmark.
%
As described in Section~\ref{sec:logistics}, the benchmark
will contains the commands \akey{(check-sat)} and \akey{(get-proof)}.
%
The solver must output the answers to both of these commands to stdout.
Output to stderr is ignored by the toolchain.

Solvers must respond to each command in the benchmark script with the
answers defined in the SMT-LIB format specification.  If the solver
outputs a proof, this proof must be an s-expression according to the
SMT-LIB standard, but otherwise the format is not specified.
%
Solvers that respond \texttt{unknown} to the \akey{check-sat} command should
respond with an error to the following \akey{get-proof} command.  Note that the
SMT-LIB conformant error result should be output to stdout.

\header{Input/Output Checker.}
The second script, \texttt{starexec\_checker\_default}, takes as input
the benchmark file name as first argument and the stdout output of the
solver script as second argument.  Note that this output will
usually start with the \texttt{unsat} result of the \akey{(check-sat)}
command, which the checker must either parse or skip.

The checker should check the proof within the output and provide the result to
stdout.
%
A result printed to stderr is ignored.
%
The first line of the proof checker result should be either \texttt{valid},
\texttt{invalid}, \texttt{holey}, \texttt{sat}, or \texttt{unknown}.
%
The answer \texttt{valid} must only be given when the checker certifies the
given proof justifies the unsatisfiability of the given benchmark.
%
A checker that returns \texttt{valid} to a satisfiable benchmark is deemed to be
unsound.
%
The answer \texttt{invalid} should be returned if the proof is errorneous or
otherwise malformed.
%
If the proof checker determines that the proof is valid but it contains holes,
i.e., steps that are not checked for correctness, the answer should be
\texttt{holey}.
%
The answer \texttt{sat} should be given if the solver claimed that the benchmark
is satisfiable, and \texttt{unknown} should be given if the solver answered
\texttt{unknown}, if it answered \texttt{unsat} but did not give a proof, or if
the solver gave an error result.

After the first line, the proof checker can provide arbitrary
\texttt{key=value} pairs.
%
These will be collected in the final result table and can include for example
information about the number of proof steps, the number of nodes in the proof,
the number of holes, the number of different proof rules, etc.

\header{Result.}
%
The result of a solver is considered \emph{erroneous} if (i) the
response to the \akey{check-sat} command is \texttt{sat} (as the
benchmark is necessarily unsatisfiable), or
%
(ii) the proof checker returns \texttt{invalid} to
the given proof.
%
Since the \prooftrack is non-competitive and we are not fixing a definition of a
valid proof, there will be no score computed for this track.
